---
title: "MyRMarkdownTeste"
author: "Julio Cesar Marques"
date: '2022-07-12'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

```{r cars, echo = TRUE}
library(shiny)
library(ggplot2)

ui <- fluidPage(
  
  # Sidebar with a slider input for number of bins
  sidebarLayout(
    sidebarPanel(
      numericInput("numeric","Qual a quantidade de randerização no gráfico?",
                   value=nrow(mtcars),min=1,max=nrow(mtcars),step=1),
      sliderInput("sliderx","Pick minimum e maximum X Values",
                  min = 100, max = 550, value = 250),
      sliderInput("slidery","Pick minimum e maximum y Values",
                  min = 100,max = 415,value = 250),
#      selectInput("carbs", "Select carb to show",
#                  choices = c('All', unique(mtcars$carb))),      
      checkboxInput("show_xlab","Show/Hide X Axis Label", value = TRUE),
      checkboxInput("show_ylab","Show/Hide Y Axis Label", value = TRUE),
      checkboxInput("show_title","Show Hide Title")
    ),
    # Show a plot of the generated distribution
    mainPanel(
      h3("Graph of Random Points"),
      plotOutput("plot", brush = "plot_brush"),
      tableOutput("data")
    )
  )
)

```

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

